A Hitchhiker's Guide to Reproducible Research" # replace with something serious

### 2021-05-21 manuscript.Rmd

<!-- researcher should begin early to enjoy most benefits -->
Reproducibility is invaluable for effective collaboration---including with your "past self".
While you may be tempted to consider reproducibility only when you are close to completing a project, we believe that upfront investment pays off in your increased productivity.
Therefore, we suggest starting early, ideally from the moment you decide to pursue a project to incorporate tools to help you achieve reproducibility gradually.
The first step towards reproducibility is to bundle all required files in one folder.
This way, you never lose anything, and you can easily share the files without missing anything.
<!-- Hands-on: Introducing RProjects-->
RStudio's _R Projects_ facilitate this concept of a project folder.
We recomend the [`here`](https://github.com/r-lib/here)[^here] package [@R-here] to refer to files, because it works consistently across different operating systems, and between R scripts and [R Markdown].
The `repro` package offers an R Studio template, which sets up a file structure that follows best practices and conventions for placing scripts and data [@rextensions].
To create one, click on:

@@

<!--Keep notes.-->
 A great tool to capture ideas or meeting notes and eventually complete entire journal articles is Markdown.
 Markdown is a lightweight text format that is very close to plain text with a minimal subset of reserved symbols for formatting instructions.
 This way, Markup does not need any specialized software for editing, it is highly fool-proof (unlike for example LaTeX) and can be ported to various document formats, such as HTML Websites, a Microsoft Word document, a typeset PDF file (for example, via LaTeX journal templates), or a Powerpoint presentation.
We suggest to use Markdown for everything, starting from simple sketches of your ideas to your scientific manuscripts[@R-rticles] and presentations[@revealjs]---and even your CV [@vitae].
To create a Markdown document, click on:

@@

Monte Carlo simulations are a crucial tool to investigate properties of a statistical model and they are routinely employed to develop or evaluate statistical models.
For example, @maccallum1999sample used Monte Carlo simulations to investigate optimal sample size for exploratory factor analysis, or @curran1996robustness studied the robustness of the $\chi^2$ test statistic under non-normal data. In Bayesian data analysis, prior predictive checks generate data from a model according to the prior distribution in order to asses whether a prior is appropriate [@gabry2019visualization].

While rather uncommon for an empirical research project, we argue that simulating data offers various benefits in the planning phase of a study.
First, you have to address and could plan for data analytic problems on a conceptual level before you made the considerable effort to acquire data [@axelrodAdvancingArtSimulation1997].
Second, if you only simulate a single dataset, you can perform a simple technical check, that is the analysis software outputs parameter estimates [@braiekTestingMachineLearning2020], e.g. when the simulated data contains missings.
Third, if you perform a Monte Carlo simulation, you may evaluate how the data analysis copes with expected data complications, e.g. non-normal data [@harrisonIntroductionMonteCarlo2010; @raychaudhuriIntroductionMonteCarlo2008].
Fourth, you can plan your resources efficiently, e.g. determine required sample size to achieve certain precision or power [@brandmaier2018precision].

A Monte Carlo simulation affords you an ideal planning opportunity.
We realize that this comes at an expensive but believe the reduction in the risk that the data is not sufficient to answer the research questions offsets the required effort.
This advantage is especially pronounced when you plan to preregister your study.
In fact, we argue that a Monte Carlo simulation can combine the analysis, sample size planning and preregistration (see [Preregistration as Code].

@@

Strict reproducibility is at stake with any code that is based on the computer's pseudo random number generator (PRNG) because random numbers will almost always differ with each execution of the code.
To consistently get the same results while preserving the pseudo-random property of the generated numbers, it is good practice to set a random seed that sets the PRNG into a restorable state, in R code: `set.seed(1235)`.
Note however that the consistency of a given seed is not necessarily maintained across different R versions because the default algorithm for generating pseudo random numbers may change (see @Peikert2019 for a demonstration with different R versions).
It is a little more complicated to achieve uncorrelated random numbers in parallelized code (e.g., when the same code is run with different portions of data in a computer cluster).
The standard random number generator (RNG) produces high quality random numbers, but is not safe to use in parallelized code (e.g., when the same code is run with different portions of data in a computer cluster).
The problem is that concurrent random number streams are correlated, because they repeat after some time.
Therefore, if you set a seed for one worker and another seed for another worker, you could end up with the same random numbers but with a phase shift.
@lecuyerGoodParametersImplementations1999 proposed a more computationally expensive RNG, designed to generate many uncorrelated streams.
While this RNG is available as a low level interface in R (with `RNGkind("L'Ecuyer-CMRG")`), we rely on the excellent parallelization framework around the [`future`-package](futureverse.org)[^futureverse] to handle this for us across all workers.

<!--
```{r}
# reproducible but unsafe in parallel code
set.seed(1235)
runif(1)
set.seed(1235)
runif(1)
```
-->
By wrapping code that uses the internal random number generator (here, the command to create a random number from the uniform distribution, `runif(1)`) with the `future` approach, we guarantee that the random numbers will differ across parallel executions of that code, will achieve a high quality of randomness, but still will be deterministic and thus reproducible:

@@

Currently, there are various templates available that guide researchers in developing data analysis plans for preregistration [@osfstandard; @socpsytemp; @howtoreplicate]. 
Still, with any natural-language representation of an analysis plan, there remains ambiguity when turning the natural language description of a given data analysis into code [@sep-ambiguity].
Here, we discuss preregistration as code (PAC) with the R package repro, which leaves no room for ambiguity.
PAC essentially reverses the process of empirical research.
Before researchers gather data, they write a reproducible, dynamically generated manuscript (see [R Markdown]) including the sections Introduction, Methods, and Results---initially based on simulated data.
Then, the source code of this manuscript serves as an unambiguous description of the analysis plan and is published as a preregistration.
One particular advantage of this approach is that you can precisely define if-else conditions under which you choose a different analytic strategy to address possible complications (e.g. to establish partial measurement invariance, when full measurement invariance is not attainable).
This approach allows for more flexibility than a traditional template based preregistration but is still well defined.

@@

One way to ensure that your analysis to works with real data is to simulate data.
We, for example, simulated data for the Machiavellism subscale of the short dark triad (SD3) and analyzed this with structural equation modelling (SEM).
The simulation showed that we have to gather at least `r minn$n_obs` observations per group to archive enough precision and that our solution to a data problem we expect (insufficient measurement invariance) introduces a bias of `r round((est_diff - true_diff)*100/true_diff, 2)`%.
These results are also visualized in Figure \@ref(fig:simulation-plot).
If you went to the trouble to simulate data, we argue that you get a preregistration almost for free.

@@

Above, we have already suggested [Markdown] as a universal and portable text format. 
R Markdown extends regular Markdown by allowing useres you to include R code chunks (in fact, arbitrary computer code; see @riedererChapter15Other) into a Markdown document.
Upon rendering of the document, the code blocks are executed and their output is dynamically inserted into the document.
This allows the creation of (conditionally) formatted text, statistical results, or figures that are guaranteed to be up-to-date because they are created every time anew as the document is rendered to its output format (e.g., presentation slides or a journal article).

@@

When you include code into an R Markdown, this code is run, and its results are included in the rendered document.
With R Markdown, you can write whole articles (`r link("https://github.com/aaronpeikert/repro-tutorial/blob/main/manuscript.Rmd", "like the one you are reading")`).
You could, in principle, even write large parts of the manuscript as part of your preregistration, i.e. the introduction, theoretical background, the method section and parts of the discussion.
If you have simulated data, you could even include fake results.
Packages like [`stargazer`](https://cran.r-project.org/web/packages/stargazer/vignettes/stargazer.pdf)[^stargazer] [@stargazer], [`apaTables`](https://dstanley4.github.io/apaTables/articles/apaTables.html)[^apaTables] [@apaTables] and [`papaja`](http://frederikaust.com/papaja_man/)[^papaja] [@papaja] help you to create dynamically generated professional looking results.
The package [`report`](https://github.com/easystats/report)[^report] [@report] is particularly noteworthy because it not only generates tables, but also a simple interpretation of the effects as actual prose (e.g it quantifies the size of an effect).
Such a dynamic document is arguably the most concrete preregistration possible.
One advantage is that writing the manuscript and writing the preregistration are no longer two distinct tasks.
Therefore a preregistration can be thought of as simply rearranging tasks that you have to do anyway.

@@

An essential aspect of a preregistration is that you have to make it public.
Of course, if you commit the preregistration to Git and upload it into a public repository, it is also public.
However, simply using GitHub as a preregistration site is not ideal.
First, you can delete your GitHub repository whenever you want.
Second, while Git meticulously records when you made which change, committing and publishing are two different steps.
Therefore, you can choose to upload to GitHub after conducting the study while still making it look like you have made the preregistration public before conducting the study.
Third, any person with some experience in Git can retroactively change the history.
You can alleviate these downsides by using zenodo.org to give a digital object identifier (DOI) to your preregistration because zenondo.org saves an unchangeable copy of your repository.
You can learn more about this in [Creating a public release].

@@

### README (optional)

@@

Note that publishing data, code, or other materials is not sufficient to allow other users to use it, modify it, or redistribute it.
For example, according to German copyright law, a repository without a license must be assumed to be protected by copyright ([UrhG[^urhg]](https://www.gesetze-im-internet.de/englisch_urhg/englisch_urhg.html), Section 1, 7, 11).
In many countries (i.e. the USA, European Union), a content creator has exclusive right to use their creation[@stoddenLegalFrameworkReproducible2009].
A license is the legal authorization of other people to use what you have created.
<!---exact copy from our previous manuscript, do we need to change? -->
In our experience, the [Creative Commons - Attribution license (CC-BY)](https://creativecommons.org/licenses/by/4.0/) is often appropriate for sharing texts, R Markdown files, generated figures, and other media (such as stimulus materials if you created them).
In contrast, scripts and any other computer code are often best shared under the [MIT license](https://opensource.org/licenses/MIT) (or similar permissive licenses).
Copyright does often not apply to data, we therefore recommend to share data with a CC0 license to clarify that you do not hold copyright to it.
Giving data another license than CC0 is often just confusing, because a license is invalid if there is no copyright.
All licenses assure maximal freedom for future users while requiring the attribution, if possible, of the original authors in derivative work.
These licenses are also in line with the recommendations by the Reproducible Research Standard [@stoddenEnhancingReproducibilityComputational2016; @stoddenEnablingReproducibleResearch2009].
A great resource to choose a license is [choosealicense.com](https://choosealicense.com).
However, no resource, including our recommendation, replaces legal advice.
<!-- plagiary end -->
It is important to get written consent from collaborators when you change/add the license.
However, if their first contribution occurs after adding a license, they give their consent by contributing.
To add a CC-BY license to your project, simply run (there are similar commands for other licenses):

@@

### Code of Conduct

@@

## Collaboration

@@

### GitHub

@@

### GitHub Issues

@@

### GitHub Pull Requests

@@

<!--I am not sure this is the right place, should we introduce this earlier? -->

A reader of a reproducible research project should be able to easily derive how it can be reproduced (ideally by a statement in your [README]).
To do that, it is often crucial to understand how different project components relate to each other and depend on each other.
For example, you cannot run an analysis without data, or you cannot render a statistical report without having the results from the statistical analysis that is reported.
Dependency tracking means that you capture and map the interrelations between all components of your analysis.
The "components" of an analysis are typically all involved files including raw data files, intermediate files (such as a preprocessed data file), and final results (such as a rendered manuscript in PDF format).
With larger projects, there is typically a higher degree of modularization because code fragments are written for re-use in other projects (or are already re-used). Also, more complicated empirical research projects may have different hypotheses that are answered with different data sets and different statistical models, such that it often makes sense to split the different analyses into different files. Reproducibility then demands the careful documentation and mapping of all necessary steps in the correct order.

Make is a build automation tool for software projects that typically are challenged by maintaing and resolving a variety of dependencies in the correct order when compiling a piece of software-
We found _Make_ to be particularly useful for our purposes for two reasons.
First, it is language-agnostic, therefore enabling us to map steps not only taken within R but also across different programming languages or other external programs.
Second, it does implement a simple yet powerful caching mechanism of results which is welcome in computing-intensive analysis often found in neuroimaging or machine learning. 
That is, Make determines automatically which branches in the dependency graph needs updating when files have changed and does not necessarily recompute or rebuild everything.

Make is build around the concept of computational recipes.
Like cooking recipes, the dish you want to create is at the top, followed by the necessary ingredients with the procedure at last.
In Make the dish is usually a file and is called "target".
The ingredients are called "requirements" and are usually also files.
The procedures are formulated as shell commands.
One (hypothetical) example is this:

@@

Modern data analysis is only feasible because researchers rely on much external software. 
The dependency on a single R package may easily create a dependency tree of more than hundred direct or indirect dependencies [@epskamp2019].
External dependencies are unavoidable but, at the same time, a major threat to long-term reproducibility.
The critical problem is the fragility of a software setup.
Many components have to fit perfectly together, and each change, e.g. a software update or bug fixe, risks that balance.
At the same time, software updates are very much necessary to remove errors or improve methodology [@epskamp2019].
Another problem is that the software environment is also variable and what works on one machine might not work on any other.
Containers directly address such issues.
Instead of leaving it to the user which software should be installed how on their computer, Docker provides all software used in an analysis, including the operating system itself.
The operating system level is important because some functionality may be passed to software layers beneath the programming language, such as calls to random number generators, linear algebra libraries and such.
Docker does this without interfering with the already installed software by using a virtual software environment that is independent of the host software environment.
Such a snapshot of the software stack is called an "image".
Packaging all needed software in such an image requires considerable amounts of storage space.
There are two major strategies helping to keep the storage requirements reasonable.
First, there is a community that maintains images for particular purposes.
For example, there are ready-made images for R, based on Ubuntu (a Linux operating system) containers [@boettigerIntroductionRockerDocker2017].
Users can then install whatever they additionally need on top of these pre-made images.
`r ifelse(is.na(container_size), "", glue::glue("The image that was used for this article uses {round(container_size, 2)}Gb of disc space."))`
Our image includes Ubuntu, R, RStudio, LaTeX as well as many R packages like the tidyverse [@tidyverse], amounting to `r installed.packages() %>% as.data.frame() %>% filter(is.na(Priority)) %>% nrow()` packages.
Second, instead of saving a binary image of the software, one can also save a container recipe, a so-called  `Dockerfile`.
This recipe is a textual description of all commands that need to be executed to recreate the image.
Such files are tiny (the `r link("https://github.com/aaronpeikert/repro-tutorial/blob/main/Dockerfile", "Dockerfile")` for this project is `r round(as.numeric(fs::file_size("Dockerfile"))/1024^1, 2)`Kb big) and are an unambiguous description of how to recreate a given container image.
However, they rely on the assumption that all software repositories will remain accessible and will continue to make available historic software versions.
For archiving, we therefore recommend that a full image is always kept (see Section on [Archiving Docker]).
With the `repro`-package adding R packages dependencies is as simple as adding them to the header under the tag `packages:`

>>>>

<!-- researcher should begin early to enjoy most benefits -->
Reproducibility is invaluable for effective collaboration---including with your "past self".

While you might be tempted to consider reproducibility only when you about to finish a project, upfront investments pay off through your increased productivity.
Therefore, we suggest starting early, ideally from the moment you decide to pursue a project to incorporate tools to help you achieve reproducibility gradually.<!--CJ The three preceding sentences belong in the introduction; this tutorial part should be more applied, less conceptual-->

The first step towards reproducibility is to bundle all required files in one folder.
This way, you never lose anything, and you can easily share the files without missing anything.
<!-- Hands-on: Introducing RProjects-->
RStudio's _R Projects_ facilitate this concept of a project folder.
We recomend the [`here`](https://github.com/r-lib/here)[^here] package [@R-here] to refer to files, because it works consistently across different operating systems, and between R scripts and [R Markdown].
The `repro` package offers an R Studio template, which sets up a file structure that follows best practices and conventions for placing scripts and data [@rextensions].
To create one, click on:

@@

<!--Keep notes.-->
 A great tool to capture ideas or meeting notes and eventually complete entire journal articles is Markdown.
 Markdown is a lightweight text format that is very close to plain text with a minimal subset of reserved symbols for formatting instructions.
 This way, Markup<!-- CJ Up or down?--> does not need any specialized software for editing, it is highly fool-proof (unlike for example LaTeX) and can be ported to various document formats, such as HTML Websites, a Microsoft Word document, a typeset PDF file (for example, via LaTeX journal templates), or a Powerpoint presentation.
We suggest to use Markdown for everything, starting from simple sketches of your ideas to your scientific manuscripts[@R-rticles] and presentations[@revealjs]---and even your CV [@vitae].
To create a Markdown document, click on:

@@

Monte Carlo simulations <!-- CJ Explain what this is! Or consider using plain language instead.--> are a crucial tool to investigate properties of a statistical model and they are routinely employed to develop or evaluate statistical models.
For example, @maccallum1999sample used Monte Carlo simulations to investigate optimal sample size for exploratory factor analysis, or @curran1996robustness studied the robustness of the $\chi^2$ test statistic under non-normal data.

While rather uncommon for an empirical research project, we argue that simulating data offers various benefits in the planning phase of a study.<!-- CJ I feel that this is a better opening paragraph, because it introduces the concept of simulating data! However, consider that some readers may have no idea of what that means, and might require even more detail.-->
First, you have to address and could plan for data analytic problems on a conceptual level before you made the considerable effort to acquire data [@axelrodAdvancingArtSimulation1997].
Second, if you only simulate a single dataset, you can perform a simple technical check, that is the analysis software outputs parameter estimates [@braiekTestingMachineLearning2020], e.g. when the simulated data contains missings.
Third, if you perform a Monte Carlo simulation, you may evaluate how the data analysis copes with expected data complications, e.g. non-normal data [@harrisonIntroductionMonteCarlo2010; @raychaudhuriIntroductionMonteCarlo2008].
Fourth, you can plan your resources efficiently, e.g. determine required sample size to achieve certain precision or power [@brandmaier2018precision].

A Monte Carlo simulation affords you an ideal planning opportunity.<!-- CJ Put the other monte carlo stuff here, and explain what it is-->
We realize that this comes at an expensive but believe the reduction in the risk that the data is not sufficient to answer the research questions offsets the required effort.<!-- CJ What are you trying to say in this sentence? -->
This advantage is especially pronounced when you plan to preregister your study.
In fact, a Monte Carlo simulation can help plan the analysis in detail, form the basis of power calculation and sample size planning, and can be preregistered integrally (see [Preregistration as Code].<!-- CJ Should this preregistration as code have been introduced earlier? There, you could discuss the notion of simulating data-->

@@

Strict reproducibility is at stake with any code that is based on the computer's pseudo random number generator (PRNG) because random numbers will almost always differ with each execution of the code.
To consistently get the same results while preserving the pseudo-random property of the generated numbers, it is good practice to set a random seed that sets the PRNG into a restorable state, in R code: `set.seed(1235)`.
Note however that the consistency of a given seed is not necessarily maintained across different R versions because the default algorithm for generating pseudo random numbers may change (see @Peikert2019 for a demonstration with different R versions).
It is a little more complicated to achieve uncorrelated random numbers in parallelized code (e.g., when the same code is run with different portions of data in a computer cluster).<!-- CJ This is probably too specialized for a paper about workflows. You have not introduced parallelization, so it doesn't make sense to talk about special provisions for paralellized code. -->
The standard random number generator (RNG) produces high quality random numbers, but is not safe to use in parallelized code (e.g., when the same code is run with different portions of data in a computer cluster).
The problem is that concurrent random number streams are correlated, because they repeat after some time.
Therefore, if you set a seed for one worker and another seed for another worker, you could end up with the same random numbers but with a phase shift.
@lecuyerGoodParametersImplementations1999 proposed a more computationally expensive RNG, designed to generate many uncorrelated streams.

While this RNG is available as a low level interface in R (with `RNGkind("L'Ecuyer-CMRG")`), we rely on the excellent parallelization framework around the [`future`-package](futureverse.org)[^futureverse] to handle this for us across all workers:<!-- CJ These are many technical terms that apply only to parallelized code; a concept you have not introduced and one that seems out of scope-->

```{r}
# reproducible but unsafe in parallel code
set.seed(1235)
runif(1)
set.seed(1235)
runif(1)
```

By wrapping code that uses the internal random number generator (here, the command to create a random number from the uniform distribution, `runif(1)`) with the `future` approach, we guarantee that the random numbers will differ across parallel executions of that code, will achieve a high quality of randomness, but still will be deterministic and thus reproducible:

@@

Currently, there are various templates available that guide researchers in developing data analysis plans for preregistration [@osfstandard; @socpsytemp; @howtoreplicate]. 
All of these templates use natural language to describe the analysis plan.
The crucial limitation of any natural-language representation of an analysis plan is that it leaves room for ambiguity when translating the plan into code [@sep-ambiguity].
Preregistration as code (PAC) addresses this limitation, by... <!-- CJ Provide definition first.-->
Here, we discuss preregistration as code (PAC) with the R package repro, which leaves no room for ambiguity.
PAC essentially reverses the process of empirical research.
Before researchers gather data, they write a reproducible, dynamically generated manuscript (see [R Markdown]) including the sections Introduction, Methods, and Results---initially based on simulated data.
Then, the source code of this manuscript serves as an unambiguous description of the analysis plan and is published as a preregistration.
One particular advantage of this approach is that you can precisely define if-else conditions under which you choose a different analytic strategy to address possible complications (e.g. to establish partial measurement invariance, when full measurement invariance is not attainable). <!-- CJ This is a great idea, but I feel like you should first explain the general concept of PAC in more detail before presenting specific benefits, like forking paths.-->
This approach allows for more flexibility <!-- CJ This is confusing, because you just said that traditional templates allowed for too much flexibility--> than a traditional template based preregistration but is still well defined.

@@

One way to ensure that your analysis to works with real data is to simulate data. <!-- CJ I'm having flashbacks to the previous paragraph about simulating data. Haven't you said this already? Merge all sections about the same topic-->
We, for example, simulated data for the Machiavellism subscale of the short dark triad (SD3) and analyzed this with structural equation modelling (SEM).
The simulation showed that we have to gather at least `r minn$n_obs` observations per group to archive enough precision and that our solution to a data problem we expect (insufficient measurement invariance) introduces a bias of `r round((est_diff - true_diff)*100/true_diff, 2)`%.
These results are also visualized in Figure \@ref(fig:simulation-plot).
If you went to the trouble to simulate data, we argue that you get a preregistration almost for free.

@@

Above, we have already suggested [Markdown] as a universal and portable text format. <!-- CJ I feel like these sections should be merged. It does not make sense to introduce markdown first, and then several pages down, introduce R Markdown.-->
R Markdown extends regular Markdown by allowing useres you to include R code chunks (in fact, arbitrary computer code; see @riedererChapter15Other) into a Markdown document.
Upon rendering of the document, the code blocks are executed and their output is dynamically inserted into the document.
This allows the creation of (conditionally) formatted text, statistical results, or figures that are guaranteed to be up-to-date because they are created every time anew as the document is rendered to its output format (e.g., presentation slides or a journal article).

@@

When you include code into an R Markdown, this code is run, and its results are included in the rendered document.
With R Markdown, you can write whole articles (`r link("https://github.com/aaronpeikert/repro-tutorial/blob/main/manuscript.Rmd", "like the one you are reading")`).
You could, in principle, even write large parts of the manuscript as part of your preregistration, i.e. the introduction, theoretical background, the method section and parts of the discussion.
If you have simulated data, you could even analyze them to include dummy results.
Packages like [`stargazer`](https://cran.r-project.org/web/packages/stargazer/vignettes/stargazer.pdf)[^stargazer] [@stargazer], [`apaTables`](https://dstanley4.github.io/apaTables/articles/apaTables.html)[^apaTables] [@apaTables] and [`papaja`](http://frederikaust.com/papaja_man/)[^papaja] [@papaja] help you to create dynamically generated professional looking results.
The package [`report`](https://github.com/easystats/report)[^report] [@report] is particularly noteworthy because it not only generates tables, but also a simple interpretation of the effects as actual prose (e.g it quantifies the size of an effect).
Such a dynamic document is arguably the most concrete preregistration possible.
One advantage is that writing the manuscript and writing the preregistration are no longer two distinct tasks.
Therefore a preregistration can be thought of as simply rearranging tasks that you have to do anyway.

@@

An essential aspect of a preregistration is that you have to make it public. <!-- CJ This requires a reference. I believe I found one that defined prereg as an "indelible, time-stamped record". That's useful-->
Of course, if you commit the preregistration to Git and upload it into a public repository, it is also public. <!-- CJ You should credit my paper for this, as I'm the first to make this argument.-->
However, simply using GitHub as a preregistration site is not ideal.
First, you can delete your GitHub repository whenever you want.
Second, while Git meticulously records when you made which change, committing and publishing are two different steps.
Therefore, you can choose to upload to GitHub after conducting the study while still making it look like you have made the preregistration public before conducting the study.
Third, any person with some experience in Git can retroactively change the history.
You can alleviate these downsides by using zenodo.org to give a digital object identifier (DOI) to your preregistration because zenondo.org saves an unchangeable copy of your repository.
You can learn more about this in [Creating a public release].<!-- CJ That's a great idea! -->

@@

### README (optional) <!-- CJ I think this is too much information about the readme file. -->

@@

Note that publishing data, code, or other materials is not sufficient to allow other users to use it, modify it, or redistribute it.
For example, according to German copyright law, a repository without a license must be assumed to be protected by copyright ([UrhG[^urhg]](https://www.gesetze-im-internet.de/englisch_urhg/englisch_urhg.html), Section 1, 7, 11).
In many countries (i.e. the USA, European Union), a content creator has exclusive right to use their creation[@stoddenLegalFrameworkReproducible2009].
A license is the legal authorization of other people to use what you have created.
<!---exact copy from our previous manuscript, do we need to change? -->
In our experience <!-- CJ This sentence should not be used in relation to legal matters. Refer to a trusted legal authority, not personal experience. -->, the [Creative Commons - Attribution license (CC-BY)](https://creativecommons.org/licenses/by/4.0/) is often appropriate for sharing texts, R Markdown files, generated figures, and other media (such as stimulus materials if you created them).
In contrast, scripts and any other computer code are often best shared under the [MIT license](https://opensource.org/licenses/MIT) (or similar permissive licenses).
Copyright does often not apply to data <!-- CJ Reference, also this is a very important point that might require some elaboration.-->, we therefore recommend to share data with a CC0 license to clarify that you do not hold copyright to it.
Giving data another license than CC0 is often just confusing, because a license is invalid if there is no copyright.
All licenses assure maximal freedom for future users while requiring the attribution, if possible, of the original authors in derivative work.
These licenses are also in line with the recommendations by the Reproducible Research Standard [@stoddenEnhancingReproducibilityComputational2016; @stoddenEnablingReproducibleResearch2009].
A great resource to choose a license is [choosealicense.com](https://choosealicense.com).
However, no resource, including our recommendation, replaces legal advice.
<!-- plagiary end -->
It is important to get written consent from collaborators when you change/add the license.
However, if their first contribution occurs after adding a license, they give their consent by contributing.<!-- CJ Is this true by default, or should it be included in your contributor guidelines or someting?-->
To add a CC-BY license to your project, simply run (there are similar commands for other licenses):

@@

### Code of Conduct <!-- CJ I have mixed feelings about this. Considering that CoC is a recent development in software communities, and that it has caused substantial debate (and some casualties) in those communities, and considering that it is not currently "a thing" in scientific communities, and considering that it does not directly relate to reproducible workflows - I sincerely doubt whether this has any place in the present tutorialn. I would recommend sticking with solutions that solve issues experienced by scientists, not by programmers.-->

@@

## Collaboration <!-- CJ This should be in the introduction - in fact, there was already a remark about it. Merge those sections -->

@@

### GitHub <!-- CJ merge this with your earlier github section -->

@@

### GitHub Issues <!-- CJ This is another example of something not essential for reproducibility; consider leavcing it out of the paper. Definitely not worth it's own header! -->

@@

### GitHub Pull Requests <!-- CJ Same, not relevant -->

@@

<!--I am not sure this is the right place, should we introduce this earlier? --> <!-- CJ Yes-->

A reader of your reproducible manuscript should be able to derive how they are to reproduce it (ideally by a statement in your [README]).
To do that, it is often crucial to understand how different project components relate to each other.
You cannot run an analysis without data; you cannot render a dynamic document without an analysis, and so forth.
Dependency tracking means that you capture the interrelations between the components of your analysis.
The "components" of an analysis are often loosely mapped onto files.
For a simple project, it might be enough to have a single R Markdown file.
However, while it is easy to understand how to reproduce the end result, this approach quickly gets unwieldy.
To better navigate the data analysis, a researcher often splits it across several scripts.
For example, they create a script to load the data and another to run the analysis.
This modularisation <!-- CJ Are you using UK or US spelling? Modularization? --> facilitates reuse because the loading script may be used by other projects building on the same data, while the analysis script may be employed on different data and so forth.
The downside is that reproducibility is complicated because instead of reproducing everything in one step, multiple steps are required.

Of course, there a several ways to solve this problem.
One could build an R package to separate analysis <!-- CJ This sentence is going to lose all readers who are not R package developers, i.e., the entire target readership--> and data or use code externalization <!-- CJ Now you're even losing me ;) --> in the RMarkdown to facilitating reuse or create a "main" script that combines all steps.
We found Make to be particularly useful for two reasons. <!-- CJ Unless I'm mistaken, Make has not yet been introduced? -->
First, it is language agnostic, therefore fusing steps that are carried out in different programming languages. <!-- CJ This is confusing, because you have not yet explained what make is / does -->
Second, it does implement a simple yet powerful caching mechanism <!-- CJ Eh?? What is this --> of results which is welcome in computing-intensive analysis often found in neuroimaging or machine learning.

Make is build around the concept of computational recipes.<!-- CJ This is better. Start with this (and add one sentence first with a definition of Make-->
Like cooking recipes, the dish you want to create is at the top, followed by the necessary ingredients with the procedure at last.
In Make the dish is usually a file and is called "target".
The ingredients are called "requirements" and are usually also files.
The procedures are formulated as shell commands. <!-- CJ This might shock you, but many readers won't know what shell commands are. -->
One (hypothetical) example is this:

@@

Modern data analysis is only feasible because researchers rely on much external software. <!-- CJ This is kind of a sweeping statement... what does it mean?-->
One downside is that a considerable number of external dependencies may hinder collaboration and long term reproducibility.
The dependency on a single R package may easily create a dependency tree of more than hundred direct or indirect dependencies [@epskamp2019].
External dependencies are unavoidable but, at the same time, a major threat to long-term reproducibility.
The critical problem is the fragility of a software setup.
Many components have to fit perfectly together, and each change, e.g. a software update or bug fixe, risks that balance.
At the same time, software updates are very much necessary to remove errors or improve methodology [@epskamp2019].
Another problem is that the software environment is also variable and what works on one machine might not work on any other.
Containers directly address such issues.
Instead of leaving it to the user which software should be installed how on their computer, Docker provides all software used in an analysis, including the operating system itself.
The operating system level is important because some functionality may be passed to software layers beneath the programming language, such as calls to random number generators, linear algebra libraries and such.
Docker does this without interfering with the already installed software by using a virtual software environment that is independent of the host software environment.
Such a snapshot of the software stack is called an "image".
Packaging all needed software in such an image requires considerable amounts of storage space.
There are two major strategies helping to keep the storage requirements reasonable.
First, there is a community that maintains images for particular purposes.
For example, there are ready-made images for R, based on Ubuntu (a Linux operating system) containers [@boettigerIntroductionRockerDocker2017].
Users can then install whatever they additionally need on top of these pre-made images.
`r ifelse(is.na(container_size), "", glue::glue("The image that was used for this article uses {round(container_size, 2)}Gb of disc space."))`
Our image includes Ubuntu, R, RStudio, LaTeX as well as many R packages like the tidyverse [@tidyverse], amounting to `r installed.packages() %>% as.data.frame() %>% filter(is.na(Priority)) %>% nrow()` packages.
Second, instead of saving a binary image of the software, one can also save a container recipe, a so-called  `Dockerfile`.
This recipe is a textual description of all commands that need to be executed to recreate the image.
Such files are tiny (the `r link("https://github.com/aaronpeikert/repro-tutorial/blob/main/Dockerfile", "Dockerfile")` for this project is `r round(as.numeric(fs::file_size("Dockerfile"))/1024^1, 2)`Kb big) and are an unambiguous description of how to recreate a given container image.
However, they rely on the assumption that all software repositories will remain accessible and will continue to make available historic software versions.
For archiving, we therefore recommend that a full image is always kept (see Section on [Archiving Docker]).
With the `repro`-package adding R packages dependencies is as simple as adding them to the header under the tag `packages:`
